\huge Fast Evaluation of Intermolecular Charge Transfer Energy: New Approach Based on One-Electron Effective Potentials

### 2019-06-28 papers/conference/1.MQM_2019/poster-84x118cm.tex
Poster revision

\begin{textblock*}{440mm}(10mm,135mm)
\begin{block}{Ab Initio Charge Transfer Energy in Fragment-Based Modelling}
 \begin{itemize}
   \item CT energy is an {\color{green} important} stabilizing contribution to the total interaction energy
   \item It is {\color{red} very costly} to compute and generally not directly included in most force fields
   \item {\color{green} EFP2 model} implements efficient CT energy estomator
   \item However, EFP2 CT energy is {\color{red} 30-40 times slower} then evaluating other components
   \item In effect, this CT term is usually {\color{red} not included} in condensed matter modelling
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{250mm}(10mm,253mm)
\begin{block}{Our Approach}
 \begin{itemize}
   \item Consider Murrell et al.'s perturbation theory
   \item Apply OEP method to eliminate ERI's
   \item Adapt the CT term to the EFP2 method
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{180mm}(270mm,253mm)
\begin{block}{CT energy by Murrell et al.}
  \vskip-2ex
  \begin{equation*}
    \Delta E_{\rm CT}^{A\rightarrow B} = 2\sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir}
     \frac{\vert V_{in}^{A\rightarrow B} \vert^2 }{\varepsilon_i - \varepsilon_n}
  \end{equation*}
  \vskip0.4ex
\end{block}
\end{textblock*}

@@

% - Scheme 
\begin{textblock*}{820mm}(10mm,341mm)
\begin{exampleblock}{Coupling Constant $\boldsymbol{ V_{in}^{A\rightarrow B} } $}
\begin{figure}
\includegraphics[width=1.0\textwidth]{scheme.eps}
\caption{\bf Application of the OEP technique to significantly simplify original theory of Murrell et al. EFP parameters
are shown in blue.}
\end{figure}
\end{exampleblock}
\end{textblock*}

@@

\begin{textblock*}{257mm}(573mm,824mm)
\begin{block}{Summary and Outlook}
 \begin{itemize}
   \item OEP-based model reproduces CT energies of the parent Murrell et al.'s [3] model.
   \item OEP-based model is 4-7 times faster than EFP2
   \item OEP's can be applied to other problems
 \end{itemize}
\end{block}
\end{textblock*}

@@

%
%
%% ----------------------- SUMMARY
%%
%
% --------------------- ACKNOWLEDGEMENTS
\begin{textblock*}{820mm}(10mm,1070mm)
\begin{block}{Acknowledgements}
 This project is carried out under POLONEZ programme which has received funding from the European Union's
 Horizon~2020 research and innovation programme under the Marie Sk{\l}odowska-Curie grant agreement 
 No.~665778. This project is funded by National Science Centre, Poland 
 (grant~no. 2016/23/P/ST4/01720) within the POLONEZ 3 fellowship.
 We thank
 Wroc{\l}aw Centre for Networking and Supercomputing (WCSS) for
 providing high quality computational resources.
\end{block}
\end{textblock*}
%
%%
%
%% --------------------- REFERENCES
%\begin{textblock*}{440mm}(10mm,1106mm)
%\begin{exampleblock}{\color{blue} References}
%    References\\
%    \begin{small}
%[1] Gordon, M. S.; Fedorov. D. G.; Pruitt, S. R.; Slipchenko L. V.; Chem. Rev., 2012, 112, 632
%[2] Murrell, J. N.; Randic, M.; Williams O. R.; Proc. Roy. Soc. A, 1965, 284, 566
%[3] Li, H.; Gordon, M. S.; J. Chem. Phys., 2006, 124, 214108
%              [2] B. B{\l}asiak, M. Maj, R. W. G{\'o}ra, M. Cho, \newline\emph{J. Chem. Theory Comput.}, 11, 3259 {\bf{\small 2015}};
%    \end{small}         
%%\end{exampleblock}
%\end{textblock*}
%
%
%
\end{frame}
\end{document}

>>>>

\begin{textblock*}{440mm}(10mm,135mm)
\begin{block}{Ab Initio Charge Transfer Energy in Fragment-Based Modelling}
 \begin{itemize}
   \item CT energy is an {\color{green} important} stabilizing contribution to the total interaction energy [1]
   \item It is {\color{red} very costly} to compute and generally not directly included in most force fields
   \item {\color{green} EFP2 model} implements efficient CT energy estomator [2,3]
   \item However, EFP2 CT energy is {\color{red} 30-40 times slower} then evaluating other components [3]
   \item In effect, this CT term is usually {\color{red} not included} in condensed matter modelling [4]
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{250mm}(10mm,253mm)
\begin{block}{Our Approach}
 \begin{itemize}
   \item Consider Murrell et al.'s perturbation theory [5]
   \item Apply OEP method to eliminate ERI's
   \item Adapt the CT term to the EFP2 method [2,3]
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{180mm}(270mm,253mm)
\begin{block}{CT energy by Murrell et al. [5]}
  \vskip-2ex
  \begin{equation*}
    \Delta E_{\rm CT}^{A\rightarrow B} = 2\sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir}
     \frac{\vert V_{in}^{A\rightarrow B} \vert^2 }{\varepsilon_i - \varepsilon_n}
  \end{equation*}
  \vskip0.4ex
\end{block}
\end{textblock*}

@@

% - Scheme 
\begin{textblock*}{820mm}(10mm,341mm)
\begin{exampleblock}{Coupling Constant $\boldsymbol{ V_{in}^{A\rightarrow B} } $}
\begin{figure}
\includegraphics[width=1.0\textwidth]{scheme.eps}
\caption{\bf Application of the OEP technique to significantly simplify original theory of Murrell et al.[5] EFP parameters
are shown in blue.}
\end{figure}
\end{exampleblock}
\end{textblock*}

@@

\begin{textblock*}{257mm}(573mm,824mm)
\begin{block}{Summary and Outlook}
 \begin{itemize}
   \item OEP-based model reproduces CT energies of the parent Murrell et al.'s [5] model
   \item OEP-based model is 4-7 times faster than EFP2
   \item Further optimization is possible: using QUAMBO orbitals [4]
   \item OEP's can be applied to other problems as well
 \end{itemize}
\end{block}
\end{textblock*}

\begin{textblock*}{257mm}(573mm,970mm)
%\begin{exampleblock}{\color{blue} References}
    References: %\\
    \begin{small}
%[1] Gordon, M. S.; Fedorov. D. G.; Pruitt, S. R.; Slipchenko L. V.; \emph{Chem. Rev.} {\bf 2012}, 112, 632
[1] Gordon, M. S. et al.; \emph{Chem. Rev.} {\bf 2012}, 112, 632 
[2] Li, H.; Gordon, M. S.; \emph{J. Chem. Phys.} {\bf 2006}, 124, 214108
[3] Xu, P.; Gordon, M. S.; \emph{J. Chem. Phys.} {\bf 2013}, 139, 194104
[4] Kaliman, I. A.; Slipchenko, L. V.; \emph{J. Comput. Chem.} {\bf 2015}, 36, 129
[5] Murrell, J. N.; Randic, M.; Williams O. R.; \emph{Proc. Roy. Soc. A} {\bf 1965}, 284, 566
    \end{small}         
%\end{exampleblock}
\end{textblock*}
\begin{textblock*}{257mm}(573mm,964mm)
\noindent\rule{83cm}{5.4pt}
\end{textblock*}

@@

%
%
%% ----------------------- SUMMARY
%%
%
% --------------------- ACKNOWLEDGEMENTS
\begin{textblock*}{820mm}(10mm,1070mm)
\begin{block}{Acknowledgements}
 This project is carried out under POLONEZ programme which has received funding from the European Union's
 Horizon~2020 research and innovation programme under the Marie Sk{\l}odowska-Curie grant agreement 
 No.~665778. This project is funded by National Science Centre, Poland 
 (grant~no. 2016/23/P/ST4/01720) within the POLONEZ 3 fellowship.
 We thank
 Wroc{\l}aw Centre for Networking and Supercomputing (WCSS) for
 providing high quality computational resources.
\end{block}
\end{textblock*}

\end{frame}
\end{document}
